GlobalSearchRegression.jl \\ \vspace{5mm} REPORT

### 2019-07-23 test/Latex/main.tex
Full integration

\begin{lstlisting} 
      using GlobalSearchRegression
      GlobalSearchRegression.gsr(
        {{#input}}
        equation = "{{equation}}",
        data = {{data}},
        datanames = {{datanames}},
        method = :{{method}},
        intercept = {{intercept}},
        {{#panel}}panel = {{.}},{{/panel}}
        {{#time}}time = {{.}},{{/time}}
        {{#seasonaladjustment}}seasonaladjustment = {{.}},{{/seasonaladjustment}}
        removeoutliers = {{removeoutliers}},
        {{/input}}

@@

{{#input}}
\subsection{Pre-processing}
It performs required variable transformations to improve model accuracy and feature selection. In this report, it has been used the following internal pre-processing functions:

@@

  {{#seasonalfortex}}
    \item Seasonal-adjustment: variables {{#:fe_seasonaladjustment_names}}{{.}}, {{/:fe_seasonaladjustment_names}}have been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}). For each one, the function removes the seasonal component using window lengths equal to {{#:fe_seasonaladjustment_vals}}{{.}}, {{/:fe_seasonaladjustment_vals}}respectively.
  {{/seasonalfortex}}

  {{#seasonalfortex2}}
  \item Seasonal-adjustment: variable {{#:fe_seasonaladjustment_names2}}{{.}}{{/:fe_seasonaladjustment_names2}} has been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}). The function removes the seasonal component using a window length equal to {{#:fe_seasonaladjustment_vals2}}{{.}}{{/:fe_seasonaladjustment_vals2}}.
  {{/seasonalfortex2}}

  {{#removeoutliers}} 
  \item Remove-outliers: extreme observations (because of input errors or extraordinary/non-relevant events) have been removed using the standard 3-sigma rule (see \cite{lehmann2013}).
  {{/removeoutliers}}
\end{enumerate}
{{/input}}
{{#featureextraction}}
\subsection{Feature extraction}

In this stage, selected functions have been used to create additional covariates with the following transformations:

\begin{enumerate}
  {{#fe_lag}}
    {{#vars}}
    \item Lags: for variables {{#names}}{{.}}, {{/names}}the lag operator created lag polinominals of order {{#values}}{{.}}, {{/values}}respectively, as additional explanatory variables.
    {{/vars}}
    {{#var}}
    \item Lags: for variable {{#names}}{{.}}{{/names}}, the lag operator created a lag polinominal of order {{#values}}{{.}}{{/values}}, as an additional explanatory variable.
    {{/var}}
  {{/fe_lag}}
  {{#fe_log}}
    {{#vars}}
    \item Logs: for variables {{#names}}{{.}}, {{/names}}the logarithm transformation was applied to generate new covariates.
    {{/vars}}
    {{#var}}
    \item Logs: for variable {{#names}}{{.}}{{/names}}, the logarithm transformation was applied to generate a new covariate.
    {{/var}}
  {{/fe_log}}
  {{#fe_inv}}
    {{#vars}}
    \item Inverse: for variables {{#names}}{{.}}, {{/names}}the inverse function was implemented to create additional covariates.
    {{/vars}}
    {{#var}}
    \item Inverse: for variable {{#names}}{{.}}{{/names}}, the inverse function was implemented to create an additional covariate.
    {{/var}}
  {{/fe_inv}}
  {{#fe_sqr}}
    {{#vars}}
    \item Squares: for variables {{#names}}{{.}}, {{/names}}the square transformation was implemented to create additional explanatory variables.
    {{/vars}}
    {{#var}}
    \item Squares: for variable {{#names}}{{.}}{{/names}}, the square transformation was implemented to create an additional explanatory variable.
    {{/var}}
  {{/fe_sqr}} 
  {{#interaction}}
    {{#vars}}
    \item Interactions: for variables {{#names}}{{.}}, {{/names}}all possible first-level interactions were created as additional covariates.
    {{/vars}}
    {{#var}}
    \item Interactions: for variable {{#names}}{{.}}{{/names}}, all possible first-level interactions were created as an additional covariate.
    {{/var}}
  {{/interaction}}
\end{enumerate}
{{/featureextraction}}
{{#preliminaryselection}}
\subsection{Regularization - LASSO}
The Least Absolute Shrinkage and Selection Operator (LASSO) algorithm is a type of regularized linear regression that uses shrinkage (see \cite{tibshirani1996}) to obtain simple sparse models. This particular type of regression is well-suited for feature selection in models with high levels of muticollinearity, and particularly efficient in fat-data scenarios.

@@

In this report, the $\lambda$ parameter has been dynamically defined in order to retain up to {{lassonumvars}} covariates.

It must be noticed that all predictors are standardized "on-the-fly", in order to avoid scale issues in feature selection.
{{/preliminaryselection}}

{{#allsubsetregression}}
\subsection{All-subset-Regression}
Unlike other feature selection algorithms (including LASSO), All-subset-regression (ASR) approaches guarantees both in-sample and out-of-sample optimality (i.e. better information criteria results than any other method). However, it has been left aside by econometricians and machine learning practitioners because of computational concerns. Execution times for ASR algorithms in a more-than-20-covariates environement were prohibitive until now. Using existing ASR packages, a simple feature selection problem for 20 covariates usually takes more than 8000 seconds in 
\href{https://cran.r-project.org/web/packages/MuMIn/MuMIn.pdf}{R}, and more than 500000 seconds in \href{https://ideas.repec.org/c/boc/bocode/s457737.html#download}{Stata}. Moreover, with 25 potential covariates both algorithms are unable to obtain feasible-solutions in standard personal computers.

@@

In this Julia package, the best model among $2^{n}-1$ alternatives is selected using a potentially composite ordering variable defined as the equally-weighted average of normalized (to guarantee equal weights) and harmonized (to ensure that higher values always identify better models) user's specified criteria. For in-sample adjustment, available alternatives include: Adjusted R2 (:r2adj, the default), Bayesian information criteria (:bic), Akaike and Corrected Akaike information criteria (:aic and :aicc), Mallows's Cp statistic (:cp), Sum of squared errors (also known as Residual sum of squares, :sse) and the Root mean square error (:rmse). For out-of-sample accuracy, there is available the out-of-sample root mean square error (:rmsout). Users are free to combine in-sample and out-of-sample information criteria. In this report, selected information criteria include ({{#criteria_names}}{{.}}, {{/criteria_names}}the key variable/s for feature selection.

@@

\begin{enumerate}
  {{#intercept}}
  \item Intercept has been included in all models. Alternatively, users could erase it by selecting the intercept=false boolean option.
  {{/intercept}}
  {{#outsample}}
  \item The outsample option identifies how many observations are used for prediction purposes. In this case, it has been set to {{outsample}}.
  {{/outsample}}
  {{#ttest}}
  \item The user's choice has been ttest=true. Therefore, standard deviation, ttest parameters and related probabilities has been calculated.
  {{/ttest}}
  {{#modelavg}}
  \item Across-models' average coefficients, t-tests and additional statistics were obtained using combined-criteria exponential weights because of the modelavg=true option. More precisely, each alternative model has a weight given by w1/sum(w1), where w1 is defined as exp(-delta/2) and delta is equal to max(index)-index -- where index is the above mentioned normalized, harmonized and potentially combined selection criteria--.
  {{/modelavg}}
  {{#residualtest}}
  \item The residualtest=true option enables white heteroskedasticity and Jarque-Bera normality test to be implemented for each model.
  {{/residualtest}}
  {{#residualtest}}
  \item The residualtest=true option enables white heteroskedasticity, Jarque-Bera normality test and the Breusch-Godfrey test for autocorrelation to be implemented for each model.
  {{/residualtest}}
  {{#orderresults}}  
  \item User's specification of orderresults=true entails that the output matrix has been sorted by the the above mentioned normalized, harmonized and potentially combined selection criteria.
  {{/orderresults}}
\end{enumerate}
{{/allsubsetregression}}

@@

{{#crossvalidation}}
\subsection{K-fold Cross Validation}

Cross-validation (CV) is a procedure used to examine feature selection robustness to re-sampling. Among different alternatives, the K-fold approach has a parameter $K$ which identifies the number of groups that a given database must be split into (see \cite{arlot2010}). In this report user selected k-fold number is {{kfolds}}.

@@

{{#time}}
For time series, however, this methodology could decrease model selection accuracy because -potential- serial correlation violate the cross-validation fundamental assumption of i.i.d. data (see \cite{bergmeir2012}). Among available alternatives, most widely used are non-dependent k-fold cross-validation (see \cite{bergmeir2018}) and rolling forecast origin cross-validation (based on \cite{hyndman2013}). Unfortunately, the  first one entails an inefficient use of available information and second one has comparison problems for the above mentioned ACV approach (because each sampling partition has a different training set size). Therefore, \verb GlobalSearchRegression.jl uses a slightly modified version of the rolling forecast origin cross-validation, with the following steps:

\begin{enumerate}
\item User defines the rolling test-set share ($s1$) and the number of sub-samples (K);
\item Therefore, the rolling training-set share ($s2$) is automatically obtained from:

\begin{equation}
  T=s1 \times T+s2 \times T+(K-1)
\end{equation}
or
\begin{equation}
  s2=(1-s1)-[(K-1)/T]
\end{equation}
where $T$ is the total number of observations.
\item Rolling sub-samples are defined using the following pseudo-code (where data is supossed to be a time-sorted matrix/array/dataframe.):

\begin{algorithm}
\caption*{\textbf{Cross validation pseudo-code 1}: Rolling sub-samples for time series}
\begin{itemize}
  \item[] for $i=1:K$
  \begin{itemize}
    \item[]  Training\_i=data[i:s2*T,:]
    \item[] Test\_i=data[(s2 \times T+i):((s2 \times T+i)+(s1 \times T)-1),:]
  \end{itemize}
  \item[] end
\end{itemize}
\end{algorithm}

\item For each sub-sample:

\begin{enumerate}
\item the first $s_{2}*T$ observations are used to train the model and the subsequent $s_{1}*T$ observations are retained to test model accuracy and compute the out-of-sample RMSE;
\item the "best candidate" (across different covariate combinations) is the model which minimizes the out-of-sample RMSE;
\end{enumerate}
\item Finally, the cross-validated best model is obtained averaging (or using median) coefficients and standard deviations across the K-best candidates.
\end{enumerate}

In this report the test size has been set to {{tsetsize}} and, as already mentioned,
selected k-fold number is {{kfolds}}.
{{/time}}
{{#panelid}}
For panel data, cross-validation techniques are similar to time-series ones, but stratified by panel-id (because panel databases can be unbalanced). More precisely, the cross-validation strategy is defined by:

\begin{enumerate}
\item As for time series, user defines the rolling test-set share ($s1$) and the number of sub-samples (K);
\item But the rolling training-set share ($s2$) is obtained from a slightly modified equation:
\begin{equation}
  \forall j, s2=(1-s1)-[(K-1)/T{j}] 
\end{equation}
where $T{j}$ is the total number of time series observations for panel-id = j.
\item Therefore, rolling sub-samples are defined as (once again, data should be time-sorted matrix/array/dataframe):

\begin{algorithm}
\caption*{\textbf{Cross validation pseudo-code 2}: Rolling sub-samples for panel data}
\begin{itemize}
    \item[] for $i=1:K$
    \begin{itemize}
        \item[]  for $j=1:Q$
        \begin{itemize}
            \item[] Training\_i\_j=data[i:s2 \times T{j},:]
            \item[] Test\_i\_j=data[(s2 \times T{j}+i):((s2 \times T{j}+i)+(s1 \times T{j})-1),:]
        \end{itemize}
        \item[] end
    \end{itemize}
    \item[] end
\end{itemize}     
\end{algorithm}

\item For each sub-sample K, the time series methodology is reproduce henceforth.
\end{enumerate}
{{/panelid}}
{{/crossvalidation}}

{{#input}}
\section{Descriptive Statistics}

@@

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset}
    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    {{#descriptive}}{{^name}}
    \hline
    \end{tabular}
\end{table}

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset (cont.)}
    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    {{/name}}{{#name}}{{name}} & Insert Description & {{nobs}} & {{mean}} & {{std}} & {{max}} & {{min}} & {{miss}}\% \\ 
    {{/name}}{{/descriptive}}\hline
    \end{tabular}
\end{table}
{{/input}}

{{#preliminaryselection}}
\section{Regularization results}

@@

\begin{table}[!h]
  \centering
  \caption{LASSO Regression results}
    \begin{tabular}{l c}
    \hline
    \hline
              & \\
    Variables & {{ depvar }} \\
    \hline
    \hline
    {{#expvars}}
      {{ name }} & {{ coef }} \\
    {{/expvars}}
    \hline
    \hline
    Observations &  {{ nobs }} \\
    \lambda      &  {{ lambda }} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/preliminaryselection}}

{{#allsubsetregression}}
\section{Global Search Regression}

@@

\begin{table}[!h]
  \centering
  \caption{GSReg results}
    {{#bestmodel}}

    \begin{tabular}{l c{{#modelavg}} c{{/modelavg}}}
    \hline
    \hline
                 &  Best Model              {{#modelavg}} & Model Averaging           {{/modelavg}} \\
    Variables    &  {{depvar}}              {{#modelavg}} & {{depvar}}                {{/modelavg}} \\
    \hline{{#bmexpvars}} 
    {{name}}     & {{best.b}}{{best.stars}} {{#avg}} & {{b}}{{stars}}    {{/avg}} \\{{#ttest}}
                 & {{best.bstd}}            {{#avg}} & {{bstd}} {{/avg}} \\{{/ttest}}
    {{/bmexpvars}}\hline

    Observations &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
    Criteria     &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
    \hline
    \hline
    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{Standard errors in parentheses} \\
    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \end{tabular}
    {{/bestmodel}}
  \label{tab:addlabel}
\end{table}

@@

{{#expvars}}
\begin{center}
    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for {{name}} }}
\end{center}

@@

\begin{figure}[!ht]
  \centering
  \begin{minipage}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{contour_{{name}}_b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.53\textwidth}
    \centering
    \includegraphics[width=\textwidth]{wireframe_{{name}}_b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}

  \begin{minipage}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Kdensity_criteria_{{name}}.png}
    \caption{Selection criteria gains for including {{name}} (Kernel view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \centering    
    \includegraphics[width=\textwidth]{BoxViolinDot_{{name}}.png}
    \caption{Selection criteria gains for including {{name}} (Box-Violin view)}    
  \end{minipage}
\end{figure}

@@

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable {{name}} Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    & {{b.avg}}      & {{t.avg}} \\
    \hline
    Median            & {{b.median}}   & {{t.median}} \\
    \hline
    Mode              & {{b.mode}}     & {{t.mode}} \\
    \hline
    Skewness          & {{b.std}}      & {{t.std}} \\
    \hline
    kurtosis          & {{b.skew}}     & {{t.skew}} \\
    \hline
    Positive Share    & {{b.kurt}}     & {{t.kurt}} \\
    \hline
    Significant Share & {{b.posshare}} & {{t.sigshare}} \\
    \hline
    \end{tabular}
\end{table}

\clearpage
{{/expvars}}

@@

In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria. For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate. Available statistics suggests that there {{are or is}} {{numofpositivegainsvariables}} explanatory {{variable or variables}} that improved model accuracy. {{Among them, {{bestvar}} or {{bestvar}}}} helps to increase up to a {{gainsinperc}}\% the user selected information criteria. On the contrary, there {{are or is}} {{numofnegativegainsvariables}} {{covariate or covariates}} that have a deleterious impact on model accuracy. This is specially true for {{worstvar}}, which seems to decrease up to a {{lossinperc}}\% the user selected information criteria}}
{{/allsubsetregression}}

{{#crossvalidation}}
\section{k-fold cross-validation}

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}} \\
                 & {{kfolds}}-fold  & {{kfolds}}-fold \\
    Variables    & Mean             & Median          \\
    \hline
    \hline
                 &                  &                  \\
                 &                  &                  \\
    \hline

>>>>

\begin{lstlisting} 
      using GlobalSearchRegression
      GlobalSearchRegression.gsr(
        equation = "y x1 x2 x3 x4 x5",
        data = dataname,
        datanames = [:y, :x1, :x2, :x3, :x4, :x5, :_cons],
        method = :fast,
        intercept = true,

        removeoutliers = true,

@@

\subsection{Pre-processing}
It performs required variable transformations to improve model accuracy and feature selection. In this report, it has been used the following internal pre-processing functions:

@@

  \item Remove-outliers: extreme observations (because of input errors or extraordinary/non-relevant events) have been removed using the standard 3-sigma rule (see \cite{lehmann2013}).
\end{enumerate}
\subsection{Regularization - LASSO}
The Least Absolute Shrinkage and Selection Operator (LASSO) algorithm is a type of regularized linear regression that uses shrinkage (see \cite{tibshirani1996}) to obtain simple sparse models. This particular type of regression is well-suited for feature selection in models with high levels of muticollinearity, and particularly efficient in fat-data scenarios.

@@

In this report, the $\lambda$ parameter has been dynamically defined in order to retain up to 6 covariates.

It must be noticed that all predictors are standardized "on-the-fly", in order to avoid scale issues in feature selection.

\subsection{All-subset-Regression}
Unlike other feature selection algorithms (including LASSO), All-subset-regression (ASR) approaches guarantees both in-sample and out-of-sample optimality (i.e. better information criteria results than any other method). However, it has been left aside by econometricians and machine learning practitioners because of computational concerns. Execution times for ASR algorithms in a more-than-20-covariates environement were prohibitive until now. Using existing ASR packages, a simple feature selection problem for 20 covariates usually takes more than 8000 seconds in 
\href{https://cran.r-project.org/web/packages/MuMIn/MuMIn.pdf}{R}, and more than 500000 seconds in \href{https://ideas.repec.org/c/boc/bocode/s457737.html#download}{Stata}. Moreover, with 25 potential covariates both algorithms are unable to obtain feasible-solutions in standard personal computers.

@@

In this Julia package, the best model among $2^{n}-1$ alternatives is selected using a potentially composite ordering variable defined as the equally-weighted average of normalized (to guarantee equal weights) and harmonized (to ensure that higher values always identify better models) user's specified criteria. For in-sample adjustment, available alternatives include: Adjusted R2 (:r2adj, the default), Bayesian information criteria (:bic), Akaike and Corrected Akaike information criteria (:aic and :aicc), Mallows's Cp statistic (:cp), Sum of squared errors (also known as Residual sum of squares, :sse) and the Root mean square error (:rmse). For out-of-sample accuracy, there is available the out-of-sample root mean square error (:rmsout). Users are free to combine in-sample and out-of-sample information criteria. In this report, selected information criteria include (the key variable/s for feature selection.

@@

\begin{enumerate}
  \item Intercept has been included in all models. Alternatively, users could erase it by selecting the intercept=false boolean option.
  \item The outsample option identifies how many observations are used for prediction purposes. In this case, it has been set to 10.
  \item The user's choice has been ttest=true. Therefore, standard deviation, ttest parameters and related probabilities has been calculated.
  \item Across-models' average coefficients, t-tests and additional statistics were obtained using combined-criteria exponential weights because of the modelavg=true option. More precisely, each alternative model has a weight given by w1/sum(w1), where w1 is defined as exp(-delta/2) and delta is equal to max(index)-index -- where index is the above mentioned normalized, harmonized and potentially combined selection criteria--.
  \item The residualtest=true option enables white heteroskedasticity and Jarque-Bera normality test to be implemented for each model.
  \item The residualtest=true option enables white heteroskedasticity, Jarque-Bera normality test and the Breusch-Godfrey test for autocorrelation to be implemented for each model.
\end{enumerate}

@@

\subsection{K-fold Cross Validation}

Cross-validation (CV) is a procedure used to examine feature selection robustness to re-sampling. Among different alternatives, the K-fold approach has a parameter $K$ which identifies the number of groups that a given database must be split into (see \cite{arlot2010}). In this report user selected k-fold number is 5.

@@

\section{Descriptive Statistics}

@@

\begin{table}[!h]
  \centering
  \caption{Descriptive Statistics for the main dataset}
    \begin{tabular}{|p{2cm}|p{4cm}|c|c|c|c|c|c|}
    \hline
    Variable & Description & Obs. & Mean & Sd & Max & Min & \% Miss \\
    \hline
    \hline
    x1 & Insert Description & 96 & -0.03 & 1.08 & 2.29 & -2.76 & 0.00\% \\ 
    x2 & Insert Description & 96 & -0.11 & 0.90 & 1.61 & -2.31 & 0.00\% \\ 
    x3 & Insert Description & 96 & -0.10 & 0.95 & 2.15 & -2.38 & 0.00\% \\ 
    x4 & Insert Description & 96 & 0.13 & 1.00 & 2.63 & -2.73 & 0.00\% \\ 
    x5 & Insert Description & 96 & -0.09 & 0.84 & 1.80 & -2.48 & 0.00\% \\ 
    _cons & Insert Description & 96 & 1.00 & 0.00 & 1.00 & 1.00 & 0.00\% \\ 
    \hline
    \end{tabular}
\end{table}

\section{Regularization results}

@@

\begin{table}[!h]
  \centering
  \caption{LASSO Regression results}
    \begin{tabular}{l c}
    \hline
    \hline
              & \\
    Variables & y \\
    \hline
    \hline
       &  \\
       &  \\
       &  \\
       &  \\
       &  \\
       &  \\
    \hline
    \hline
    Observations &  96 \\
    \lambda      &   \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}

\section{Global Search Regression}

@@

\begin{table}[!h]
  \centering
  \caption{GSReg results}

    \begin{tabular}{l c c}
    \hline
    \hline
                 &  Best Model               & Model Averaging            \\
    Variables    &  y               & y                 \\
    \hline 
    x1     & -0.121***  & -0.126***     \\
                 &              & 0.103  \\

    x2     &   & -0.012***     \\
                 &              & 0.118  \\

    x3     & 0.108*  & 0.109*     \\
                 &              & 0.114  \\

    x4     & 0.169*  & 0.152*     \\
                 &              & 0.111  \\

    x5     &   & -0.083***     \\
                 &              & 0.136  \\

    _cons     & 0.142*  & 0.146*     \\
                 &              & 0.109  \\
    \hline

    Observations &   \multicolumn{ 1  }{c}{ } \\
    Criteria     &   \multicolumn{ 1  }{c}{ } \\
    \hline
    \hline
    \multicolumn{ 2  }{c}{Standard errors in parentheses} \\
    \multicolumn{ 2  }{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \end{tabular}
  \label{tab:addlabel}
\end{table}

@@

\begin{center}
    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
\end{center}

@@

\begin{figure}[!ht]
  \centering
  \begin{minipage}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{contour__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.53\textwidth}
    \centering
    \includegraphics[width=\textwidth]{wireframe__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}

  \begin{minipage}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
    \caption{Selection criteria gains for including  (Kernel view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \centering    
    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
    \caption{Selection criteria gains for including  (Box-Violin view)}    
  \end{minipage}
\end{figure}

@@

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    &       &  \\
    \hline
    Median            &    &  \\
    \hline
    Mode              &      &  \\
    \hline
    Skewness          &       &  \\
    \hline
    kurtosis          &      &  \\
    \hline
    Positive Share    &      &  \\
    \hline
    Significant Share &  &  \\
    \hline
    \end{tabular}
\end{table}

\clearpage
\begin{center}
    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
\end{center}

\begin{figure}[!ht]
  \centering
  \begin{minipage}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{contour__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.53\textwidth}
    \centering
    \includegraphics[width=\textwidth]{wireframe__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}

  \begin{minipage}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
    \caption{Selection criteria gains for including  (Kernel view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \centering    
    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
    \caption{Selection criteria gains for including  (Box-Violin view)}    
  \end{minipage}
\end{figure}

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    &       &  \\
    \hline
    Median            &    &  \\
    \hline
    Mode              &      &  \\
    \hline
    Skewness          &       &  \\
    \hline
    kurtosis          &      &  \\
    \hline
    Positive Share    &      &  \\
    \hline
    Significant Share &  &  \\
    \hline
    \end{tabular}
\end{table}

\clearpage
\begin{center}
    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
\end{center}

\begin{figure}[!ht]
  \centering
  \begin{minipage}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{contour__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.53\textwidth}
    \centering
    \includegraphics[width=\textwidth]{wireframe__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}

  \begin{minipage}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
    \caption{Selection criteria gains for including  (Kernel view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \centering    
    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
    \caption{Selection criteria gains for including  (Box-Violin view)}    
  \end{minipage}
\end{figure}

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    &       &  \\
    \hline
    Median            &    &  \\
    \hline
    Mode              &      &  \\
    \hline
    Skewness          &       &  \\
    \hline
    kurtosis          &      &  \\
    \hline
    Positive Share    &      &  \\
    \hline
    Significant Share &  &  \\
    \hline
    \end{tabular}
\end{table}

\clearpage
\begin{center}
    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
\end{center}

\begin{figure}[!ht]
  \centering
  \begin{minipage}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{contour__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.53\textwidth}
    \centering
    \includegraphics[width=\textwidth]{wireframe__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}

  \begin{minipage}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
    \caption{Selection criteria gains for including  (Kernel view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \centering    
    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
    \caption{Selection criteria gains for including  (Box-Violin view)}    
  \end{minipage}
\end{figure}

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    &       &  \\
    \hline
    Median            &    &  \\
    \hline
    Mode              &      &  \\
    \hline
    Skewness          &       &  \\
    \hline
    kurtosis          &      &  \\
    \hline
    Positive Share    &      &  \\
    \hline
    Significant Share &  &  \\
    \hline
    \end{tabular}
\end{table}

\clearpage
\begin{center}
    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
\end{center}

\begin{figure}[!ht]
  \centering
  \begin{minipage}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{contour__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.53\textwidth}
    \centering
    \includegraphics[width=\textwidth]{wireframe__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}

  \begin{minipage}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
    \caption{Selection criteria gains for including  (Kernel view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \centering    
    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
    \caption{Selection criteria gains for including  (Box-Violin view)}    
  \end{minipage}
\end{figure}

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    &       &  \\
    \hline
    Median            &    &  \\
    \hline
    Mode              &      &  \\
    \hline
    Skewness          &       &  \\
    \hline
    kurtosis          &      &  \\
    \hline
    Positive Share    &      &  \\
    \hline
    Significant Share &  &  \\
    \hline
    \end{tabular}
\end{table}

\clearpage
\begin{center}
    \large{\textbf{Coefficient, t-test and selection criteria gains distributions for  }}
\end{center}

\begin{figure}[!ht]
  \centering
  \begin{minipage}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{contour__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.53\textwidth}
    \centering
    \includegraphics[width=\textwidth]{wireframe__b_t.png}
    \caption{Bivariate Kernel density (Contour view)}
  \end{minipage}

  \begin{minipage}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Kdensity_criteria_.png}
    \caption{Selection criteria gains for including  (Kernel view)}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \centering    
    \includegraphics[width=\textwidth]{BoxViolinDot_.png}
    \caption{Selection criteria gains for including  (Box-Violin view)}    
  \end{minipage}
\end{figure}

\begin{table}[!h]
    \centering
    \caption{Statistics}
    \begin{tabular}{|l|c|c|}
    \hline
    Variable  Statistics &  Coefficient Distribution &  T-test Distribution  \\
    \hline
    \hline
    Simple average    &       &  \\
    \hline
    Median            &    &  \\
    \hline
    Mode              &      &  \\
    \hline
    Skewness          &       &  \\
    \hline
    kurtosis          &      &  \\
    \hline
    Positive Share    &      &  \\
    \hline
    Significant Share &  &  \\
    \hline
    \end{tabular}
\end{table}

@@

In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria. For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate. Available statistics suggests that there   explanatory  that improved model accuracy.  or }} helps to increase up to a \% the user selected information criteria. On the contrary, there    that have a deleterious impact on model accuracy. This is specially true for , which seems to decrease up to a \% the user selected information criteria}}

\section{k-fold cross-validation}

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}} \\
                 & 5-fold  & 5-fold \\
    Variables    & Mean             & Median          \\
    \hline
    \hline
                 &                  &                  \\
                 &                  &                  \\
    \hline

    Error out-sample &     &   \\
    Error in-sample  &     &   \\
                     &     &   \\
    \hline
    \hline
    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
